---
title: "Biology Letters Manuscript Figures"
output: html_notebook
---

Compiling all the data and code required to produce the figures for manuscript submitted to Biology Letters.

Results exploring the effects of resolved cephalopod functional groups on predator-prey size relationships and ecosystem structure & function.
This was achieved by comparing a control model (cephalopods parametrised the same as fish excepth for min & max. sizes) to models where feeding traits (PPMR) were adjusted to represent cephalopod feeding (Feeding Only) and to models where feeding and growth were adjusted to better represent the cephalopod functional groups (Feeding + Growth).

```{r}
library(tidyverse)
# library(janitor)
library(plotrix)
```

# Figure 1: Predator-prey size relationships - Emergent trophic allometries and mean prey size panel plot

Create conceptual diagram

## Figure XX: Predator-prey size relationships

```{r}
# Read in modelled relative trophic position data
df_RTP <- read.csv("df_Figure_1_Trophic_Allometry_Model_Results.csv")[,-1]

glimpse(df_RTP)
```

```{r}
  # Read in empirical trophic level data
  df_emp_SIA <- read_csv("df_emp_SIA.csv")
  # Make copy
  df_emp_SIA_rel_ <- df_emp_SIA
  
glimpse(df_emp_SIA_rel_)
```


```{r}
  df_emp_SIA_rel <- df_emp_SIA_rel_ %>%
  mutate(name = recode(name, "Inactive Cephs" = "Low Activity","Active Cephs" ="High Activity"))
  
  #####
  # Rescale empirical RTP for active cephs
  df_emp_active <- df_emp_SIA_rel %>%
    filter(name == "High Activity")
  
  model_lm_emp_active <- lm(RTP ~ log10(Predator_Size), data = df_emp_active)
  
  df_active <- df_RTP %>%
    filter(Func_Group == "High Activity")
  
  min_emp_RTP_active <- model_lm_emp_active$coefficients[1] + (model_lm_emp_active$coefficients[2] * log10(min(df_emp_active$Predator_Size)))
  
  model_lm_active <- lm(Median_RTP ~ log10(Predator_Size), data = df_active)
  
  df_model_min_RTP <- df_active %>%
    filter(Predator_Size_Class == 111 | Predator_Size_Class == 112) %>%
    # filter(Predator_Size_Class == 220 | Predator_Size_Class == 221) %>%
    mutate(avg_min_RTP = mean(Median_RTP))
  
  min_mod_RTP_active <- df_model_min_RTP$avg_min_RTP[1]
  
  rescale_RTP_active_val <- min_mod_RTP_active - min_emp_RTP_active
  
  pos_val_active <- sqrt(rescale_RTP_active_val * rescale_RTP_active_val)
  
  
  #####
  # Rescale empirical RTP for inactive group
  df_emp_inactive <- df_emp_SIA_rel %>%
    filter(name == "Low Activity")
  
  df_inactive <- df_RTP %>%
    filter(Func_Group == "Low Activity")
  
  
  model_lm_emp_inactive <- lm(RTP ~ log10(Predator_Size), data = df_emp_inactive)
  
  min_emp_RTP_inactive <- model_lm_emp_inactive$coefficients[1] + (model_lm_emp_inactive$coefficients[2] * log10(min(df_emp_inactive$Predator_Size)))
  
  
  df_model_min_RTP_inactive <- df_inactive %>%
    filter(Predator_Size_Class == 111 | Predator_Size_Class == 112) %>%
    # filter(Predator_Size_Class == 220 | Predator_Size_Class == 221) %>%
    mutate(avg_min_RTP = mean(Median_RTP))
  
  min_mod_RTP_inactive <- df_model_min_RTP_inactive$avg_min_RTP[1]
  
  rescale_RTP_inactive_val <- min_mod_RTP_inactive - min_emp_RTP_inactive
  
  pos_val_inactive <- sqrt(rescale_RTP_inactive_val * rescale_RTP_inactive_val)
  
  Act_rescale_val <-  pos_val_active
  
  Inact_rescale_val <- pos_val_inactive 
  
  df_emp_inactive$RTP_rescaled <- df_emp_inactive$RTP + Inact_rescale_val
  
  df_emp_active$RTP_rescaled <- df_emp_active$RTP + Act_rescale_val
  
  df_zoom <- df_RTP %>%
    filter(Predator == "Low Activity" | Predator ==  "High Activity")
  
  df_RTP_plot <- df_RTP
  

df_emp_active <- df_emp_active %>% 
    mutate(name = case_when(
                            name == 'High Activity' ~ "high activity"))  

df_emp_inactive <- df_emp_inactive %>% 
    mutate(name = case_when(
                            name == 'Low Activity' ~ "low activity")) 
    

df_RTP_plot <- df_RTP_plot %>%
    mutate(Func_Group = case_when(Func_Group == 'Zooplankton' ~ "zooplankton",
                            Func_Group == 'Low Activity' ~ "low activity",
                            Func_Group == 'High Activity' ~ "high activity",
                            Func_Group == 'Fish' ~ "fish"))

RTP_plot_v2 <-
  df_RTP_plot %>% 
    mutate(Func_Group = factor(Func_Group)) %>% 
    mutate(name = fct_relevel(Func_Group, 'zooplankton','low activity','high activity','fish')) %>%
    # mutate(name = fct_relevel(Predator, 'Zooplankton','Low Activity','High Activity','Fish')) %>%
    ggplot(aes(x=Predator_Size, y= Median_RTP, colour=name, fill=name)) +
    # scale_colour_manual(values = c( "#F8766D", "#00BFC4","#C77CFF", "#7CAE00")) +
    scale_colour_manual(values = c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333")) +
    scale_fill_manual(values = c("#CCCCCC" , "#01cbfeff","#FE5455ff", "#666333")) +
   
    geom_line(linewidth=1) +
  # geom_point(size = .2) +
    # geom_smooth(method="lm", size=1) +
    ylim(2, 7.1) +
    # xlim(-8, 6) +
   # xlab(expression(paste("Body Mass"~(10^X~g)))) +
  xlab("predator mass (g)") +
  labs(col = "functional group")+
  labs(tag = "(b)", size = 14) +
  # labs(tag = "A", size = 10) +
  ylab("relative trophic position") +
    # geom_smooth(method = "lm", size=1.5, alpha = 0, linetype = "dashed") +
    #facet_wrap(~Species_Order, scales = "free_x") +
    geom_point(aes(x=Predator_Size, y= RTP_rescaled, colour=name),data = df_emp_active, size = 0.5, show.legend = F) +
  # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name),linetype="dashed", method = "lm", data = df_emp_active, size = 1, alpha = 0.1, show.legend = F) +
    # geom_smooth(aes(x=Predator_Size, y= RTP), data = df_emp_active,  method = "lm", size = 1, alpha = 0.4,linetype = "dashed", colour="black") +
    # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name), data = df_emp_active,  method = "lm", size = 1.5, alpha = 0.25,linetype = "longdash") +
    
    geom_point(aes(x=Predator_Size, y= RTP_rescaled, colour=name),data = df_emp_inactive, size = 0.5, show.legend = F) +
  # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name),linetype="dashed", method = "lm", data = df_emp_inactive, size = 1, alpha = 0.1, show.legend = F) +
   geom_ribbon(aes(ymin = Min_RTP, ymax = Max_RTP), linetype= "dashed", alpha = 0.25,size = 0.35, show.legend = F) +
    # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name), data = df_emp_inactive,  method = "lm", size = 1.5, alpha = 0.25,linetype = "twodash") +
    # geom_smooth(aes(x=Predator_Size, y= RTP), data = df_emp_inactive,  method = "lm", size = 1, alpha = 0.4,linetype = "dashed", colour="grey52") +
    scale_x_log10(limits =c(10^-5,10^6), breaks = c(1e-3, 1e+0,1e+3,1e+6), labels = c("1e-3", "1e+0","1e+3","1e+6")) +
  
    # scale_x_log10() +
    # scale_y_log10() +
    # ggtitle(label = "Community-level RTP Fixed-rescaling: Ceph FGs empirical fit (dots and solid lines) vs model output (dashed lines)") +
    theme_classic() +
    theme(
      plot.tag = element_text(face='italic'),
      axis.title = element_text(size=14),
       # axis.title.x = element_blank(),
      # axis.text.x=element_text(colour="black", size = 12),
      axis.text=element_text(colour="black", size = 13)) +
    theme(legend.key.size = unit(1, 'lines'),
          legend.position=c(0.2,0.8),
          legend.text = element_text(size=14),
          # axis.title.x  = element_blank(),
          legend.title = element_text(size=14))

RTP_plot_v2
```



```{r}
Fig_1_pA <-
  df_RTP_plot %>%
    mutate(Func_Group = case_when(Func_Group == 'Zooplankton' ~ "zooplankton",
                            Func_Group == 'Low Activity' ~ "low activity",
                            Func_Group == 'High Activity' ~ "high activity",
                            Func_Group == 'Fish' ~ "fish")) %>% 
    mutate(name = fct_relevel(Func_Group, 'zooplankton','low activity','high activity','fish')) %>%
    # mutate(name = fct_relevel(Predator, 'Zooplankton','Low Activity','High Activity','Fish')) %>%
    ggplot(aes(x=Predator_Size, y= Median_RTP, colour=name, fill=name)) +
    # scale_colour_manual(values = c( "#F8766D", "#00BFC4","#C77CFF", "#7CAE00")) +
    
   scale_colour_manual(values = c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333")) +
  scale_fill_manual(values = c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333")) +
  # scale_colour_manual(values = c("#C77CFF" ,  "#00BFC4","#F8766D","#7CAE00")) +
  #   scale_fill_manual(values = c("#C77CFF" , "#00BFC4","#F8766D", "#7CAE00")) +
   
    # geom_line(size=.5) +
  # geom_point(size = .2) +
    # geom_smooth(method="lm", size=1) +
    ylim(2, 7.1) +
    # xlim(-8, 6) +
   # xlab(expression(paste("Body Mass"~(10^X~g)))) +
  xlab("predator mass (g)") +
  labs(col = "functional group")+
  labs(tag = "(a)", size = 14) +
  # labs(tag = "A", size = 10) +
   # ylab(expression(trophic~position~symbol('\256'))) +
  ylab("trophic position") +
    # geom_smooth(method = "lm", size=1.5, alpha = 0, linetype = "dashed") +
    #facet_wrap(~Species_Order, scales = "free_x") +
    # geom_point(aes(x=Predator_Size, y= RTP_rescaled, colour=name),data = df_emp_active, size = 0.25, show.legend = F) +
  # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name),linetype="dashed", method = "lm", data = df_emp_active, size = 1, alpha = 0.1, show.legend = F) +
    # geom_smooth(aes(x=Predator_Size, y= RTP), data = df_emp_active,  method = "lm", size = 1, alpha = 0.4,linetype = "dashed", colour="black") +
    # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name), data = df_emp_active,  method = "lm", size = 1.5, alpha = 0.25,linetype = "longdash") +
    
    # geom_point(aes(x=Predator_Size, y= RTP_rescaled, colour=name),data = df_emp_inactive, size = 0.25, show.legend = F) +
  # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name),linetype="dashed", method = "lm", data = df_emp_inactive, size = 1, alpha = 0.1, show.legend = F) +
   # geom_ribbon(aes(ymin = Min_RTP, ymax = Max_RTP), linetype= "dashed", alpha = 0.25,size = 0.35, show.legend = F) +
    # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name), data = df_emp_inactive,  method = "lm", size = 1.5, alpha = 0.25,linetype = "twodash") +
    # geom_smooth(aes(x=Predator_Size, y= RTP), data = df_emp_inactive,  method = "lm", size = 1, alpha = 0.4,linetype = "dashed", colour="grey52") +
    # scale_x_log10(limits =c(10^-5,10^6)) +
  scale_x_continuous(limits =c(-10,120), breaks = c(1,100)) +
    # ggtitle(label = "Community-level RTP Fixed-rescaling: Ceph FGs empirical fit (dots and solid lines) vs model output (dashed lines)") +
    theme_classic() +
  
    theme(
      plot.tag = element_text(face="italic"),
      # axis.ticks.x = element_blank(),
      axis.title = element_text(size=14),
       # axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      # axis.text.x=element_text(colour="black", size = 8),
      axis.text=element_text(colour="black", size = 13)) +
    theme(legend.position="none") +
  annotate("text", label = "activity level", x= 18.5, y = 6.85, size = 5) +
  annotate("text", label = "low", x= 4.4, y = 6.2, colour = "#01cbfeff", size = 5) +
  annotate("text", label = "high", x= 5.5, y = 6.5, colour = "#FE5455ff", size = 5)


library(png)
library(grid)



png_1 <- readPNG("Fig_1_Panel_A_v1.png")
g <- rasterGrob(png_1, interpolate = TRUE)

Fig_1_pA <- Fig_1_pA + annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf)


Fig_1_pA
```

```{r}
feeding_kernel_beta <- function(Species, w_min, w_max, beta, sigma, df_prey_w){
  
  df_prey_w <- df_prey_w$df_w
  Species <- Species
  w_min <- w_min
  w_max <- w_max
  beta  <- beta
  sigma <- sigma
      
    # Feeding level across prey sizes at minimum predator size  
    fk_value <- exp(-0.5*(log((beta*df_prey_w)/
                                            w_min)/sigma)^2)/
        sqrt(2*pi*sigma^2)
    
    df_min <- as.data.frame(fk_value)
    df_min$w_prey <- df_prey_w
    df_min$Predator_Size <- "1 g"
    df_min$Species <- Species
    
    # Feeding level across prey sizes at maximum predator size 
    fk_value <- exp(-0.5*(log((beta*df_prey_w)/
                                            w_max)/sigma)^2)/
        sqrt(2*pi*sigma^2)
    
    df_max <- as.data.frame(fk_value)
    df_max$w_prey <- df_prey_w
    df_max$Predator_Size <- "100 g"
    df_max$Species <- Species
    
df_plot <- do.call("rbind", list(df_min, df_max))
df_plot$Predator_Size <- as.factor(df_plot$Predator_Size)
df_plot$Species <- as.factor(df_plot$Species)
df_plot$Type <- "Beta"
df_plot$Type <- as.factor(df_plot$Type)

write.csv(df_plot, paste(Species,"fk_df.csv"))

}
```


```{r}
feeding_kernel_mode <- function(Species, w_min, w_max, m, sigma, df_prey_w){
  
  df_prey_w <- df_prey_w$df_w
  Species <- Species
  w_min <- w_min # Minimum size of predator species/func group
  w_max <- w_max # Maximum size of predator species/func group
  m     <- m     # Feeding mode value
  sigma <- sigma # Width of feeding kernel
  
      D.z_min <- 2*(3*w_min*1e12/(4*pi))^(1/3) # convert body mass g to ESD (um)
      betas_min =  (exp(0.02*log(D.z_min)^2 - m + 1.832))^3 # Calculates PPMR for minimum size predator of species[i]
      
      D.z_max <- 2*(3*w_max*1e12/(4*pi))^(1/3) # convert body mass g to ESD (um)
      betas_max =  (exp(0.02*log(D.z_max)^2 - m + 1.832))^3 # Calculates PPMR for maximum size predator of species[i]
      
      
    fk_value <- exp(-0.5*(log((betas_min*df_prey_w)/
                                            w_min)/sigma)^2)/
        sqrt(2*pi*sigma^2)  # Calculates the min size feeding kernel (feeding level of  min size predator at every size class of prey)
    
    df_min <- as.data.frame(fk_value)
    df_min$w_prey <- df_prey_w
    df_min$Predator_Size <- "1 g"
    df_min$Species <- Species
    
    
    fk_value <- exp(-0.5*(log((betas_max*df_prey_w)/
                                            w_max)/sigma)^2)/
        sqrt(2*pi*sigma^2)  # Calculates the max size feeding kernel (feeding level of  max size predator at every size class of prey)
    
    df_max <- as.data.frame(fk_value)
    df_max$w_prey <- df_prey_w
    df_max$Predator_Size <- "100 g"
    df_max$Species <- Species
    
df_plot <- do.call("rbind", list(df_min, df_max))
df_plot$Predator_Size <- as.factor(df_plot$Predator_Size)
df_plot$Species <- as.factor(df_plot$Species)
df_plot$Type <- "Mode"
df_plot$Type <- as.factor(df_plot$Type)

write.csv(df_plot, paste(Species,"fk_df.csv"))

}

```


```{r}

# df_prey_w <- read.csv("df_weight.csv")
# 
# feeding_kernel_mode("low activity", 10^0, 10^2, 0, 2, df_prey_w)
# feeding_kernel_beta("high activity", 10^0, 10^2, 25, 2, df_prey_w)

```


```{r}

df_fk_la <- read.csv("Low Activity fk_df.csv")
df_fk_ha <- read.csv("high activity fk_df.csv")

df_fk_plot <- rbind(df_fk_la, df_fk_ha)


Fig_1_pC <-
df_fk_plot %>%
  mutate(Predator_Size = factor(Predator_Size)) %>% 
  ggplot(aes(x=w_prey, y= fk_value, colour = Species, linetype = Predator_Size)) +
  labs(col = "functional group")+
  labs(linetype = "predator mass") +
  xlab("prey mass (g)") +
  labs(tag = "(c)", size = 14) +
  # labs(tag = "A", size = 10) +
  ylab("predator diet proportion") +
  geom_line(size = 1) +
    # geom_smooth(method = "lm", size=1.5, alpha = 0, linetype = "dashed") +
    #facet_wrap(~Species_Order, scales = "free_x") +
    # geom_point(aes(x=Predator_Size, y= RTP_rescaled, colour=name),data = df_emp_active, size = 0.25, show.legend = F) +
  # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name),linetype="dashed", method = "lm", data = df_emp_active, size = 1, alpha = 0.1, show.legend = F) +
    # geom_smooth(aes(x=Predator_Size, y= RTP), data = df_emp_active,  method = "lm", size = 1, alpha = 0.4,linetype = "dashed", colour="black") +
    # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name), data = df_emp_active,  method = "lm", size = 1.5, alpha = 0.25,linetype = "longdash") +
    
    # geom_point(aes(x=Predator_Size, y= RTP_rescaled, colour=name),data = df_emp_inactive, size = 0.25, show.legend = F) +
  # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name),linetype="dashed", method = "lm", data = df_emp_inactive, size = 1, alpha = 0.1, show.legend = F) +
   # geom_ribbon(aes(ymin = Min_RTP, ymax = Max_RTP), linetype= "dashed", alpha = 0.25,size = 0.35, show.legend = F) +
    # geom_smooth(aes(x=Predator_Size, y= RTP, colour=name), data = df_emp_inactive,  method = "lm", size = 1.5, alpha = 0.25,linetype = "twodash") +
    # geom_smooth(aes(x=Predator_Size, y= RTP), data = df_emp_inactive,  method = "lm", size = 1, alpha = 0.4,linetype = "dashed", colour="grey52") +
    scale_colour_manual(values = c("#FE5455ff","#01cbfeff"), guide = "none") +
    # scale_colour_discrete(guide = "none") + 
    scale_y_continuous(limits =c(0,0.5), breaks = c(0,0.25, 0.5)) +
    scale_x_log10(limits =c(2e-6,100), breaks = c(2e-5, 3e-4,0.04,4), labels = c("2e-5", "3e-4","0.04","4")) +
    geom_segment(aes(x = 0.04, y = 0.21, xend = 4, yend = 0.21),
               arrow = arrow(length = unit(0.2, "cm"), ends = "both"), colour="black", size = 1, show.legend = F) +
    geom_segment(aes(x = 2e-5, y = 0.21, xend = 3e-4, yend = 0.21),
               arrow = arrow(length = unit(0.2, "cm"), ends = "both"), colour="black", size = 1, show.legend = F) +
    # ggtitle(label = "Community-level RTP Fixed-rescaling: Ceph FGs empirical fit (dots and solid lines) vs model output (dashed lines)") +
    theme_classic() +
    theme(
      plot.tag = element_text(face = 'italic'),
      # axis.ticks.x = element_blank(),
      axis.title = element_text(size=14),
       axis.text.x = element_text(colour="black", size = 13),
      axis.text.y = element_text(colour="black", size = 13),
      # axis.ticks.y = element_blank(),
      # axis.text.x=element_text(colour="black", size = 8),
      # axis.text=element_text(colour="black", size = 14),
      legend.key.size = unit(1, 'lines'),
          legend.position=c(0.275,0.8),
          legend.text = element_text(size=14),
          # axis.title.x  = element_blank(),
          legend.title = element_text(size=14))
    # theme(legend.position="none") +
  # annotate("text", label = "predator mass", x= 2e-5, y = 0.9) +
  # annotate("text", label = "1 g", x= 3e-4, y = 0.85) +
  # annotate("text", label = "100 g", x= 3e-4, y = 0.8)

# png_2 <- readPNG("C:/Users/kjmurphy/OneDrive - University of Tasmania/Thesis Figures/Conceptual Diagram/Fig_1_Panel_C_v1.png")
# g2 <- rasterGrob(png_2, interpolate = TRUE)
# 
# Fig_1_pC <-  Fig_1_pC + annotation_custom(g2, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf)

Fig_1_pC
```



```{r}

# df_ref <- tibble(
#   Predator_Size = c(min(df_plot_PPMR_Full$Predator_Size), max(df_plot_PPMR_Full$Predator_Size))
# )
# df_ref$Expected_prey_size = 0.005882353*df_ref$Predator_Size

df_PPMR_plot <- read.csv("PPMR_plot_F+G_combined_results.csv")


PPMR_plot_v2 <-
  df_PPMR_plot %>% 
  mutate(name = case_when(name == 'Zooplankton' ~ "zooplankton",
                            name == 'Low Activity' ~ "low activity",
                            name == 'High Activity' ~ "high activity",
                            name == 'Fish' ~ "fish")) %>% 
    mutate(name = fct_relevel(name, 'zooplankton','low activity','high activity','fish')) %>%
  ggplot(aes(x = Predator_Size, y = Median_N, color = name)) +
  # geom_line(data = df_ref, aes(x = Predator_Size, y = Expected_Prey_Size_PPMR1),
  #             linetype = "solid", size = 0.75) +
  #   geom_line(data = df_ref, aes(x = Predator_Size, y = Expected_Prey_Size_PPMR10),
  #             linetype = "longdash", size = 0.75) +
  #   geom_line(data = df_ref, aes(x = Predator_Size, y = Expected_Prey_Size_PPMR100),
  #             linetype = "dashed", size = 0.75) +
  #   geom_line(data = df_ref, aes(x = Predator_Size, y = Expected_Prey_Size_PPMR1000),
  #             linetype = "twodash", size = 0.75) +
  #   geom_line(data = df_ref, aes(x = Predator_Size, y = Expected_Prey_Size_PPMR10000),
  #             linetype = "dotdash", size = 0.75) +
  #   geom_line(data = df_ref, aes(x = Predator_Size, y = Expected_Prey_Size_PPMR100000),
  #             linetype = "dotted", size = 0.75) +
    geom_line(size = 1, show.legend = F) +
     labs(col = "functional group")+
  
    # geom_segment(aes(x = min(Predator_Size), xend = max(Predator_Size), y = (min(Predator_Size)* 0.01010101), yend = (max(Predator_Size)* 0.01010101)), linetype = "dotted", colour = "#FE5455ff", size=1) +
    # geom_segment(aes(x = min(Predator_Size), xend = max(Predator_Size), y = (min(Predator_Size)*  0.0009775171), yend = (max(Predator_Size)*  0.0009775171)), linetype = "dotted", colour = "#666333", size=1) + ## Barnes dataset realised PPMR value for ectotherm vertebrates
  
  geom_segment(aes(x = 10e-5, xend = max(Predator_Size), y = (10e-5* 0.01010101), yend = 10e5 * 0.01010101), linetype = "dotted", colour = "#FE5455ff", size=1) +
    geom_segment(aes(x = 10e-5, xend = max(Predator_Size), y = (10e-5*  0.0009775171), yend = (max(Predator_Size)*  0.0009775171)), linetype = "dotted", colour = "#666333", size=1) + ## Barnes dataset realised PPMR value for ectotherm vertebrates
  
    # geom_segment(aes(x = min(Predator_Size), xend = max(Predator_Size), y = (min(Predator_Size)*.01), yend = (max(Predator_Size)*.01)), linetype = "longdash", colour = "black", size=0.5) +
    # scale_colour_manual(values = c( "#F8766D", "#00BFC4","#C77CFF", "#7CAE00")) +
    scale_colour_manual(values = c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333")) +
    scale_fill_manual(values = c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333")) +
    geom_ribbon(aes(ymin = Min_N, ymax = Max_N, fill = name), alpha = 0.25, linetype = "dashed",show.legend = F, size = 0.35) +
    # scale_x_log10() +
    scale_x_log10(limits =c(10^-5,10^6), breaks = c(1e-3, 1e+0,1e+3,1e+6), labels = c("1e-3", "1e+0","1e+3","1e+6")) +
    scale_y_log10(limits =c(10^-9,10^4.5)) +
    labs(tag = "(d)", size = 14) +
    # facet_wrap( ~ Predator) +
    labs(x = "predator mass (g) ", y = "mean prey mass (g)") +
    # annotate(angle = 48, "text", label= "PPMR = 170", x = 10^-10.2, y = 10^-11.5, size = 3.5) +
    annotate(angle = 37, "text", label= "PPMR = 99", x = 10e-5, y = 10^-5.3, size = 4.5, colour = "#FE5455ff",fontface = 2) + # If using Barnes realised PPMR for cephalopods of 99
  # annotate(angle = 33, "text", label= "PPMR = 99", x = 10^-10.2, y = 10^-11.7, size = 3.75, colour = "#FE5455ff",fontface = 2) + # If using Barnes realised PPMR for cephalopods of 99
    annotate(angle = 35, "text", label= "PPMR = 1023", x = 10e-5, y = 10^-7.5, size = 4.5,colour = "#666333",fontface = 2) + # If using Barnes realised PPMR for cephalopods of 1023 ectotherm vertebrates
    coord_cartesian(clip = 'off') +  # This keeps the labels from disappearing
    theme_classic() + 
    theme(legend.key.size = unit(1, 'lines'),
          legend.position=c(0.25,0.8),
          legend.background = element_blank(),
          axis.title = element_text(size=14, colour = "black"),
          axis.text = element_text(size=13, colour = "black"),
           # axis.title.x = element_blank(),
          plot.tag = element_text(face = 'italic'),
      # axis.text.x=element_text(colour="black", size = 12),
      # axis.text.y=element_text(colour="black", size = 12),
      legend.title=element_text(size=14), 
      legend.text=element_text(size=14))
```



```{r}
library(patchwork)
Fig_1_pA + RTP_plot_v2 + Fig_1_pC + PPMR_plot_v2 +  plot_layout(widths = c(1,1.4))

# ggsave("Figure_1_v3.png",
#        units="mm",
#        dpi = 600,
#        width = 240,
#        height =240)
```

## Figure 2: Ecosystem Metrics

Read in raw data with Control, Feeding-Only, and Feeding+Growth model sets

```{r}
df_fig_XX_raw <- read.csv("Community_Metrics_Figure_XX.csv")

glimpse(df_fig_XX_raw)
```

Inspect dataframe

```{r}
df_fig_XX_tidy <- df_fig_XX_raw %>% 
  mutate(Model = factor(Model),
         Group = factor(Group),
         Level = factor(Level),
         Variant = factor(Variant))

glimpse(df_fig_XX_tidy)
```
Calculate the difference between metrics across the model sets to provide a summary value for effect size

```{r}
df_effect_size <- df_fig_XX_tidy %>% 
  filter(Level == "Community") %>% 
  filter(Metric == "Total Biomass (g m3)"|Metric == "Mean P:B"|Metric == "1/Community_CV"|Metric == "Production") %>% 
  group_by(Model, Metric) %>% 
  summarise(mean_value = mean(Value),
            se_value = std.error(Value))
  
df_effect_size
# write.csv(df_effect_size, "community_metric_effect_size.csv")
```

Boxplot for desired ecosystem metrics
```{r}
df_fig_XX_tidy %>% 
  filter(Level == "Community") %>% 
  filter(Metric == "Total Biomass (g m3)"|Metric == "Mean P:B"|Metric == "1/Community_CV"|Metric == "Production") %>% 
  ggplot(aes(x=Model,
             y = Value)) +
  geom_violin() +
  facet_wrap(~Metric, scales = "free_y")
  scale_y_log10()
  
```


```{r}
phyto_min <- -14.5
phyto_max <- -7.9
a <- -1.3
b <- -0.88

df_plot_ <- read.csv("Feeding+Growth_Abundance_SizeSpec_Figure_XX.csv")

df_control <- read.csv("df_comb_SizeSpec_Plot_Control_Model.csv")

df_plot_control <- df_control %>%
   mutate(Func_Group = recode(Predator, Zoo='Zooplankton',  "Inactive Cephs" = "Low Activity","Active Cephs" ="High Activity", Fish="Fish"))

df_plot_control_inactive <- df_plot_control %>%
  filter(Func_Group == "Low Activity") %>%
   filter(log10(Median_N) > -11)

df_plot_control_active <- df_plot_control %>%
  filter(!Func_Group == "Low Activity") %>%
   filter(log10(Median_N) > -11)


df_plot_active_cutoff <- df_plot_ %>%
  filter(Func_Group == "High Activity") %>%
   filter(log10(Median_N) > -11)


df_plot_inactive_cutoff <- df_plot_ %>%
  filter(Func_Group == "Low Activity") %>%
   filter(log10(Median_N) > -11)


df_plot_zoo_cutoff <- df_plot_ %>%
  filter(Func_Group == "Zooplankton") %>%
   filter(log10(Median_N) > -11)

df_plot_fish_cutoff <- df_plot_%>%
  filter(Func_Group == "Fish") %>%
   filter(log10(Median_N) > -11)


df_path1 <- df_plot_control_inactive %>% 
  mutate(Func_Group = case_when(Func_Group == 'Zooplankton' ~ "zooplankton",
                                                            Func_Group == 'Low Activity' ~ "low activity",
                                                            Func_Group == 'High Activity' ~ "high activity",
                                                            Func_Group == 'Fish' ~ "fish")) %>% 
  mutate(Func_Group = fct_relevel(Func_Group, 'zooplankton','low activity','high activity','fish'))

df_path2 <- df_plot_control_active %>% 
  mutate(Func_Group = case_when(Func_Group == 'Zooplankton' ~ "zooplankton",
                                                            Func_Group == 'Low Activity' ~ "low activity",
                                                            Func_Group == 'High Activity' ~ "high activity",
                                                            Func_Group == 'Fish' ~ "fish")) %>% 
  mutate(Func_Group = fct_relevel(Func_Group, 'zooplankton','low activity','high activity','fish'))


pA <- df_plot_ %>%
  filter(log10(Median_N) > -11) %>%
  mutate(Func_Group = case_when(Func_Group == 'Zooplankton' ~ "zooplankton",
                            Func_Group == 'Low Activity' ~ "low activity",
                            Func_Group == 'High Activity' ~ "high activity",
                            Func_Group == 'Fish' ~ "fish")) %>% 
    mutate(Func_Group = fct_relevel(Func_Group, 'zooplankton','low activity','high activity','fish')) %>%
  # mutate(Func_Group = fct_relevel(Func_Group,'Zooplankton', "Low Activity", "High Activity", "Fish")) %>%
  # mutate(Functional_Group = Species_Order) %>%
ggplot(aes(x =log10(Predator_Size), y = log10(Median_N), colour = Func_Group)) + 
  labs(col = "functional group")+
    geom_path(size=1.25) +
    # geom_path(data = df_plot_FO_, aes(), linetype = "dotdash", size=1) +
    geom_path(data = df_path1, aes(), linetype="dotted", size=1.25) +
  geom_path(data = df_path2, aes(), linetype="dashed", size=1.25) +
    xlab(expression(paste("body mass"~(10^X~g)))) +
     ylab(expression(abundance~(10^X~"m"^-3)))+
  scale_colour_manual(values = c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333")) +
    scale_fill_manual(values = c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333")) +
  # c("#CCCCCC" ,  "#01cbfeff","#FE5455ff","#666333"))
  labs(tag = "(a)", size = 12) +
  # labs(subtitle = "Feeding + Growth Model Abundance Size Spectra") +
  geom_ribbon(aes(ymin = log10(Min_N), ymax = log10(Max_N), fill = Func_Group), colour=NA, alpha = 0.25, linetype = "dashed", show.legend = F, size = 0.25) +
  xlim(-15,6) +
    #geom_point(aes(x=log(df_mode_norm_biomass$size_class), y=log(df_mode_norm_biomass$normalised_biomass), colour = df_mode_norm_biomass$Feeding_mode)) +
    #stat_smooth(method = "lm", col = "black", linetype = "longdash", alpha = F, size=0.5) +
    geom_segment(aes(x = phyto_min , xend = phyto_max, y = (a) + (b*phyto_min), yend = a + (b*phyto_max)), colour="green",linetype="dotted", size = 1.25) +
    # labs(title = paste("Normalised Biomass Size Spectra: ", scenario,
    #                    "\nFixed Phytoplankton Resource Size Spectrum (Green Dash)", "Intercept =", projection$environ$a,
    #                    " Slope =", projection$environ$b,
    #                    "\nLinear slope of dynamic community =",round(fit_v1$coefficients[2], 2))) +
    theme_classic() +
    # scale_colour_manual(name = 'Functional Group',
    #                     values =c("#C77CFF", "#F8766D", "#00BFC4","#7CAE00"), labels = c('Zooplankton','Active','Inactive', 'Fish')) +
    theme(plot.title = element_text(size = 12)) +
    theme(
      plot.tag = element_text(face="italic"),
      axis.title = element_text(size=12),
      # axis.title.x = element_blank(),
      # axis.text.x=element_text(colour="black", size = 10),
      axis.text=element_text(colour="black", size = 12)) +
    theme(legend.key.size = unit(1, 'lines'),
          legend.position=c(0.15,0.3),
          legend.text = element_text(colour="black", size = 12),
          legend.title  = element_text(colour="black", size = 12))

png_x <- readPNG("Fig 2 Legend addition.png")
g_x <- rasterGrob(png_x, interpolate = TRUE)

pA <- pA + annotation_custom(g_x, xmin=-15.7, xmax=-11, ymin=0, ymax=4.8)

pA
```


```{r}
library(patchwork)
library(ggforce)

Model_Sets <- c("control", "F + G")

df_Eco_Plot <- df_fig_XX_tidy %>%
  filter(Level == "Func Group") %>% 
  mutate(Func_Group=recode(Group, Zoo='zooplankton',  Inactive= "low activity", Active ="high activity", Fish="fish"))

df_Violin_plot <- df_fig_XX_tidy %>% 
  filter(Level == "Community")

```


```{r}

pB <- df_Violin_plot %>%
  # mutate(Fishing_Level = fct_relevel(Fishing, 'None', 'Low','High')) %>%
  mutate(Eco_Metric = fct_relevel(Metric, 'Total Biomass (g m3)','Fish:Community Biomass','FCL','Mean P:B','Biomass weighted PPMR', "Mean PPMR", "Mean FG CV", "Community CV", 'Mean TTE', 'Biomass weighted TTE')) %>%
  # mutate(Func_Group = fct_relevel(Group,'Zoo', "Low Activity", "High Activity", "Fish")) %>%
  # mutate(Model = fct_relevel(Model, 'Control','Control Sigma', 'Ceph', 'Energetics',  'Sigma', 'SE')) %>%
  filter(Model == "Control" | Model == "Feeding"| Model == "Feeding + Growth") %>%
  filter(Level == "Community") %>%
    # filter(Remove == "N") %>%
    # filter(Repro == "Dynamic") %>%
   # filter(Model == "Simple"|Model == "Ceph") %>%
  # filter(Fishing_Level == "None") %>%
  # filter(Metric == "Total Biomass (g m3)" | Metric == "Fish:Community Biomass"| Metric == "Fish P:B"| Metric =="Biomass weighted PPMR"|Metric == "Biomass weighted TTE"|Metric == "Fish Biomass (g m3)") %>%
  filter(Metric == "Total Biomass (g m3)") %>%
ggplot(aes(x = Model, y=Value, fill = Model, linetype = Model), width =2) +
  scale_fill_manual(values = c("grey" ,  "violet")) +
  # labs(title = "Dynamic Repro") +
  geom_violin(show.legend = F,lwd=0.5) +
  scale_linetype_manual(values = c("longdash" , "solid")) +
  scale_x_discrete(labels= Model_Sets) +
  stat_summary(fun.y="median", shape=23, 
                 geom="point", size=2,show.legend = F) +
  labs(tag = "(b)", size = 12) +
  ylab(expression(paste("biomass"~("g m"^-3))))+
  # scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9")) +
  # facet_wrap(~Metric, scales = "free_y") +
  theme_classic(base_size = 12) +
  theme(strip.text = element_blank(),
        plot.tag = element_text(face="italic"),
        axis.text.x = element_text(angle = 90),
        axis.title = element_text(size=12),
        axis.title.x = element_blank(),
        axis.text = element_text(size=12))

pD <- df_Violin_plot %>%
  # mutate(Fishing_Level = fct_relevel(Fishing, 'None', 'Low','High')) %>%
  mutate(Eco_Metric = fct_relevel(Metric, 'Total Biomass (g m3)','Fish:Community Biomass','FCL','Mean P:B','Biomass weighted PPMR', "Mean PPMR", "Mean FG CV", "Community CV", 'Mean TTE', 'Biomass weighted TTE', 'Community Production')) %>%
  # mutate(Func_Group = fct_relevel(Group,'Zoo', "Low Activity", "High Activity", "Fish")) %>%
  # mutate(Model = fct_relevel(Model, 'Control','Control Sigma', 'Ceph', 'Energetics',  'Sigma', 'SE')) %>%
  filter(Model == "Control" | Model == "Feeding"| Model == "Feeding + Growth") %>%
  filter(Level == "Community") %>%
    # filter(Remove == "N") %>%
    # filter(Repro == "Dynamic") %>%
   # filter(Model == "Simple"|Model == "Ceph") %>%
  # filter(Fishing_Level == "None") %>%
  # filter(Metric == "Total Biomass (g m3)" | Metric == "Fish:Community Biomass"| Metric == "Fish P:B"| Metric =="Biomass weighted PPMR"|Metric == "Biomass weighted TTE"|Metric == "Fish Biomass (g m3)") %>%
  filter(Metric == "1/Community_CV") %>%
ggplot(aes(x = Model, y=Value, fill = Model, linetype = Model), width =2) +
  scale_fill_manual(values = c("grey" ,  "violet")) +
  scale_linetype_manual(values = c("longdash" , "solid")) +
  # labs(title = "Dynamic Repro") +
  geom_violin(show.legend = F, lwd=0.5) +
  scale_x_discrete(labels= Model_Sets) +
  stat_summary(fun.y="median", shape=23, 
                 geom="point", size=2,show.legend = F) +
  labs(tag = "(d)", size = 12) +
  # ylab(expression(paste("log"[10]~" CV")))+
  ylab("1/CV")+
  # scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9")) +
  # facet_wrap(~Metric, scales = "free_y") +
  theme_classic(base_size = 12) +
  theme(strip.text = element_blank(),
        plot.tag = element_text(face="italic"),
        axis.text.x = element_text(angle = 90),
        axis.title = element_text(size=12),
        axis.title.x = element_blank(),
        axis.text = element_text(size=12))

pE <- df_Violin_plot %>%
  # mutate(Fishing_Level = fct_relevel(Fishing, 'None', 'Low','High')) %>%
  mutate(Eco_Metric = fct_relevel(Metric, 'Total Biomass (g m3)','Fish:Community Biomass','FCL','Mean P:B','Biomass weighted PPMR', "Mean PPMR", "Mean FG CV", "Community CV", 'Mean TTE', 'Biomass weighted TTE', 'Community Production')) %>%
  # mutate(Func_Group = fct_relevel(Group,'Zoo', "Low Activity", "High Activity", "Fish")) %>%
  # mutate(Model = fct_relevel(Model, 'Control','Control Sigma', 'Ceph', 'Energetics',  'Sigma', 'SE')) %>%
  filter(Model == "Control" | Model == "Feeding"| Model == "Feeding + Growth") %>%
  filter(Level == "Community") %>%
    # filter(Remove == "N") %>%
    # filter(Repro == "Dynamic") %>%
   # filter(Model == "Simple"|Model == "Ceph") %>%
  # filter(Fishing_Level == "None") %>%
  # filter(Metric == "Total Biomass (g m3)" | Metric == "Fish:Community Biomass"| Metric == "Fish P:B"| Metric =="Biomass weighted PPMR"|Metric == "Biomass weighted TTE"|Metric == "Fish Biomass (g m3)") %>%
  filter(Metric == "Mean P:B") %>%
ggplot(aes(x = Model, y=(1/Value), fill = Model, linetype = Model), width =2) +
  scale_fill_manual(values = c("grey" , "violet")) +
  scale_linetype_manual(values = c("longdash" , "solid")) +
  scale_x_discrete(labels= Model_Sets) +
  # labs(title = "Dynamic Repro") +
  geom_violin(show.legend = F, lwd=0.5) +
  stat_summary(fun.y="median", shape=23, 
                 geom="point", size=2,show.legend = F) +
  labs(tag = "(e)", size = 12) +
  ylab("turnover time (years)")+
  # scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9")) +
  # facet_wrap(~Metric, scales = "free_y") +
  theme_classic(base_size = 12) +
  theme(strip.text = element_blank(),
        plot.tag = element_text(face="italic"),
        axis.text.x = element_text(angle = 90),
        axis.title = element_text(size=12),
        axis.title.x = element_blank(),
        axis.text = element_text(size=12))

pC <- df_Violin_plot %>%
  filter(Metric == "Production") %>%
  # mutate(Func_Group = fct_relevel(Group,'Zoo', "Low Activity", "High Activity", "Fish")) %>%
  # mutate(Model = fct_relevel(Model, 'Control','Control Sigma', 'Ceph', 'Energetics',  'Sigma', 'SE')) %>%
  # filter(Model == "Control" | Model == "Feeding"| Model == "Feeding + Growth") %>%
  filter(Model == "Control" | Model == "Feeding + Growth") %>%
  filter(Level == "Community") %>%
    # filter(Remove == "N") %>%
    # filter(Repro == "Dynamic") %>%
   # filter(Model == "Simple"|Model == "Ceph") %>%
  # filter(Fishing_Level == "None") %>%
  # filter(Metric == "Total Biomass (g m3)" | Metric == "Fish:Community Biomass"| Metric == "Fish P:B"| Metric =="Biomass weighted PPMR"|Metric == "Biomass weighted TTE"|Metric == "Fish Biomass (g m3)") %>%
  ggplot(aes(x = Model, y=Value, fill = Model, linetype = Model), width =2) +
  scale_linetype_manual(values = c("longdash" , "solid")) +
  scale_x_discrete(labels= Model_Sets) +
  scale_fill_manual(values = c("grey" , "violet")) +
  # labs(title = "Dynamic Repro") +
  geom_violin(lwd=.5, show.legend = F) +
  stat_summary(fun.y="median", shape=23,
                 geom="point", size=2,show.legend = F) +
  labs(tag = "(c)", size = 12) +
  ylab(expression(paste("production"~("g m"^-3))))+
  ylim(0.025,0.028) +
  # scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9")) +
  # facet_wrap(~Metric, scales = "free_y") +
  theme_classic(base_size = 12) +
  theme(strip.text = element_blank(),
        plot.tag = element_text(face="italic"),
        axis.text.x = element_text(angle = 90),
        axis.title = element_text(size=12),
        axis.title.x = element_blank(),
        axis.text = element_text(size=12)) #+
  # theme(legend.key.size = unit(1, 'lines'),
  #         legend.position=c(0.85,0.8),
  #         legend.background = element_blank(),
  #     legend.title=element_text(size=8),
  #     legend.text=element_text(size=6))

pA/(pB|pC |pD |pE) + plot_layout(nrow = 2, heights = c(1.5,1))


# ggsave("Figure_2_Bio_Letters_200_200mm.png",
#        units="mm",
#        dpi = 600,
#        width = 200,
#        height = 200)

```


